Spfy: distributed predictive genomics of E.coli with graph based result linkage

### 2017-08-18 paper-webserver.tex
ADD: more on data storage
ADD: another para on data storage

\subsection{Data Storage}
% para
% 0. Goals: big-data, everything linked, easy addition of new links
% 1. spfy is built around graph technologies
% 1. how we structure our graph
% 2. ontoogies used
% 3. inferencing
% 3 1/2. SPARQL queries

Graph databases focus on describing the relationships between different data points, is one of the emerging \cite{de2015trends} database types used for biological data, and is one of the core building blocks of a semantic web stack \cite{horrocks2005semantic}.
Spfy uses the RDFLib Python library \url{https://rdflib.readthedocs.org/} to represent all data meant for long-term storage.
When serotyping, VF, AMR predictions, and pangenome generation tasks are completed, the results are stored within the graph database.

@@

>>>>

\subsection{Data Storage}
% para
% 0. Goals: big-data, everything linked, easy addition of new links
% 1. spfy is built around graph technologies
% 1. how we structure our graph
% 2. ontoogies used
% 3. inferencing
% 3 1/2. SPARQL queries
Graph databases focus on describing relationships between different data points, is one of the emerging \cite{de2015trends} database types used for biological data, and one of the core building blocks of a semantic web technology stack \cite{horrocks2005semantic}.
Spfy uses the RDFLib Python library \url{https://rdflib.readthedocs.org/} to represent all data meant for long-term storage.
When serotyping, VF, AMR predictions, and pangenome generation tasks are completed, the results are stored within the graph database.
% note: below is a feature in development
The permanent storage of results serve as a one-time cost, and allows population-wide analyses of all stored genomes; result storage also enables Spfy to avoid recomputation when the same analysis is re-run.

% para
% ontology
Ontologies are indices which define types of data and the relations between them.
Spfy describes genomes as a collection of contiguous sequences (contigs), and connects the predicted genes and pangenome regions to the contigs they were found on.
(see Figure \ref{fig-ontology})
Individual genes and pangenome regions are connected to all the contigs they are found on, such that it is possible to infer all the genomes which contain a particular target sequence.

\begin{figure}[t]
\begin{center}
\includegraphics{images/spfy_ontology-1.svg}
\end{center}
\caption{Caption for figure within column.}
\label{fig-ontology}
\end{figure}

blah...

@@

(see Figure \ref{fig-docker})

\begin{figure}[t]
\begin{center}
\includegraphics{images/docker.svg}
\end{center}
\caption{Caption for figure within column.}
\label{fig-docker}
\end{figure}
